Ms 1

### 2017-09-15 ms1/ms1_display.Rmd
added appropriateness

>>>>

To compute appropriateness, I classified each PDE with the maximum appropriateness of all its linked diagnoses. I put PDEs with no associated infectious disease (i.e., FD) diagnoses into their own, lower tier.

## Trends in appropriateness

Just by eye, it looks like the changes in appropriateness are small.

```{r approp_graph}
pde_approp_table = read_tsv('tables/pde_approp_table.tsv') %>%
  filter(year %in% c(2011, 2014)) %>%
  (function(df) bind_rows(
    df,
    df %>% group_by(year, tier) %>%
      summarize(n=sum(n)) %>%
      mutate(antibiotic='overall')
  )) %>%
  filter(antibiotic %in% c(top_abx, 'overall')) %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

pde_approp_table %>%
  ggplot(aes(x=factor(year), y=f, fill=factor(tier))) +
  geom_bar(stat='identity') +
  facet_grid(~antibiotic) +
  theme_classic()
```

I'll focus on tier 1 and 2 because the SSTI drugs don't have common tier 1 uses. I'll call this "high tier" prescribign. If prescribing had changed in an optimal way, only low-tier prescribing would have declined, or only high-tier prescribing would have been added.

If a drug declined by $X$, then the optimal change in the high tier fraction would be $1/(1-X) \approx 1+X$. For example, overall prescribing fell by about 5%, and high-tier prescribing increased by 2.5%. Azithromycin prescribing fell by about 20%, and high-tier azithro prescribing rose by only 6%.

I'm not sure what to make of these results, because they depend strongly on how you define the tiers. If you use only tier 1 to describe "appropriate", then levofloxacin has the biggest decline in appropriateness, but if you use tiers 1 and 2, then it's change isn't significant.

```{r pre_approp_table}
pde_approp_trends = read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(or=exp(3*estimate), adj.p=p.adjust(p.value, method='BH')) %>%
  select(antibiotic, or, adj.p)

pde_approp_table %>%
  filter(tier <= 2) %>%
  select(antibiotic, year, f) %>%
  group_by(antibiotic, year) %>%
  summarize(f=sum(f)) %>%
  ungroup() %>%
  spread(year, f) %>%
  left_join(pde_approp_trends, by='antibiotic') %>%
  mutate(raw_pct_change=(`2014`-`2011`)/`2011`,
         adj_pct_change=risk_ratio_f(or, `2011`) - 1) %>%
  mutate_at(vars(`2011`, `2014`, raw_pct_change, adj_pct_change),
            function(x) round(x*100, 2)) %>%
  select(antibiotic, `2011`, `2014`, raw_pct_change, adj_pct_change, adj.p) %>%
  arrange(desc(`2011`)) %>%
  kable
```

And, to be more careful, I show the answer to a similar question but using a regression to correct for covariates:

```{r pde_approp_trends}

```
